Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2016-02-05 paper.tex
adjust flow fig caption

\begin{figure}[!h]
    \centering
    \includegraphics[keepaspectratio=true,width=0.45\textwidth,height=.89\textheight]{exp2/flow.eps}
    \caption[Material flow paths]{
        Material flow paths between facility types. The DU source is separate
        from enrichment tails for modeling simplicity, although enrichment
        tails could be used for added realism.  The primary fissile isotope in
        the fissile separations stream is $_{239}Pu$.
    }
    % response to technical comment 9
    \label{fig:flow}
\end{figure}

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[keepaspectratio=true,width=0.45\textwidth,height=.89\textheight]{exp2/flow.eps}
    \caption[Material flow paths]{
        Material flow paths between facility types. An independent DU source separate
        from enrichment tails is used for simplicity.  The primary fissile isotope in
        the fissile separations stream is $^{239}Pu$.
    }
    % response to technical comment 9
    \label{fig:flow}
\end{figure}
